|

### 2020-09-08 paper.Rmd
add next para
notes from meeting; first draft of discussion

@@

- better idea of size of cluster cause not bunching 
- rescale = FALSE

@@

In this paper we have introduced the sage display, as a visualisation technique for reversing
the curse of dimensionality in high dimensional projections, and have shown its utility in applications to analysis tasks found in the natural sciences and machine learning. Our case studies highlight that sage display can reduce the effects of overplotting - in the sketches example our new display decreases the number of overlapping points between classes and provides
better visual separation between classes compared to the regular tour. Furthermore, unlike some
non-linear dimension reduction techniques like t-SNE, the sage display still gives the viewer an accurate assessment of the size of a cluster, as we saw in our single cell example. Our parameter tuning example highlights that the sage display is linear up to a given effective dimension. As a result, the sage dispaly provides interpretable visualisations while preserving global structure in the high dimensional space, as highlighted in the particle physics example.

>>>>

- use four panel set up for grand tour and sage
- render pngs in addition to the gifs

@@

- better idea of size of cluster cause not bunching 
- rescale = FALSE, use principal components
- try multiple overlapping cluster example

@@

In this paper we have introduced the sage display, as a visualisation technique for reversing
the curse of dimensionality in high dimensional projections, and have shown its utility in applications to analysis tasks found in the natural sciences and machine learning. Our case studies highlight that sage display can reduce the effects of overplotting - in the sketches example our new display decreases the number of overlapping points between classes and provides
better visual separation between classes compared to the regular tour. Furthermore, unlike some
non-linear dimension reduction (NLDR) techniques like t-SNE, the sage display still gives the viewer an accurate assessment of the size of a cluster, as we saw in our single cell example. Our parameter tuning example highlights that the sage display is linear up to a given effective dimension. As a result, the sage dispaly provides interpretable visualisations while preserving global structure in the high dimensional space, as highlighted in the particle physics example.

For the sage display tuning is often required to avoid bunching points in the visualisation, especially if the projection is dense in the center of the distribution. However, given that the display is quick to compute, it is easy to try out different parameter combinations. Expanding around the center too aggresively can also introduce distortions in the display, which is also a problem for NLDR methods.

Currently, the sage display is naive information in high dimensional space that is not captured by linear projections. Further work is required to investigate other transformations of the projections that can capture non-linear structure or that are locally linear, like the transformations performed by t-SNE.
